\textls[-0]{\thetitle}

### 2023-03-06 metatheory2.tex
Working on Canonicity Appendix.

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers.

@@

>>>>

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers. Moreover, the linkage transformer can be considered as a syntactic sugar (or library functions) (we will show why at the end). 
Since it is a syntactic sugar, we will not consider about the linkage transformers during meta-theoretic reasoning.

@@

\subsection{Linkage Transformer as Syntax Sugar}
Observe the syntax, linkage transformer and its judgement is defined above 
other parts.

So we can inductively define the syntax sugar $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ using constructors $\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$. Then we define the $\inh{h}{\ell}$ and the explicit substitution for linkage transformer $\sub{h}{\gm}$ by induction on the structure of linkage transformer $h$, based on the equality given in the syntax. In that way, the explicit substituon for linkage transformer becomes meta-level substitution again; and $\inh{h}{\ell}$ is not itself a syntax but a meta-level computation that leads to a syntax.
